The Community Land Model, version 5.1 \\ One-at-a-time Parameter Perturbation Ensemble

### 2023-05-22 ms/ms.tex

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/ET_response.pdf}
\caption{(a) Global evapotranspiration in the warm forcing scenario vs. our control experiment. The response to warming with default parameters is ET+8.8\% (highlighted with the orange line). The shading spans the default ET, plus or minus 1 W/m2.
(b) The top 8 parameters governing global ET in the control experiment.
(c) The top 8 parameters governing ET response to the future climate anomaly forcing (AF2095).
Parameters governing the response to temperature anomalies tend to differ from the parameters controlling present-day ET.}
\label{fig:et}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{../figs/ET_response.png}
\caption{(a) Global annual average evapotranspiration (ET) in the warm forcing scenario vs. our control experiment. The shading spans the default ET in the control experiment, $\pm$1 W/m2. The response of ET to future climate with default parameters is +8.8\%. The orange line shows the expected future ET should the model conform to the default ET response. 
(b) The top 8 parameters governing global ET in the control experiment.
(c) The top 8 parameters governing ET response to future climate, i.e. the ratio of future ET to control ET.
Parameters governing the change in ET expected in the future tend to differ from the parameters controlling present-day ET.}
\label{fig:et}
\end{figure}
